Controlling the dewetting morphologies of thin liquid films by switchable substrates

### 2022-12-14 Reply_RefereeB.tex

\item[ \textbf{\underline{Comment 4.}}]
{
An important parameter in the problem is the wave-vector $q_0$, which sets the correlation length in the problem. 
The authors should state what the actual value is relative to either the average film height, or the wave-length of modulations. 
Is there any reason to give the wave-length of modulations in units of the system size, i.e., are the results subject to finite size effects? Otherwise it appears more meaningful to describe the modulations in units of $q_0$ or the equilibrium film thickness.
}

\item[ \textbf{{Answer}}]
{
We apologize for not giving the value of $q_0 \approx 0.09$ (corresponding to an intrinsic correlation length 
$\lambda_s = 2\pi/q_0 \approx 70 h_0$), which is now provided in the revised manuscript. We also acknowledge that expressing the wavelength in terms of the size $L$
was not at all meaningful (no finite size effects are involved). In fact, all the lengths (including $L$) are expressed in units of the mean film thickness $h_0$ (and it was so also in the old version of the paper, as commented in the text below eq. (4)). In order to avoid any confusion, we explicitly write 
the values of all lengths in terms of $h_0$ in the revised version.
}

\item[ \textbf{\underline{Comment 5.}}]
{
The thin film equation relies on a local approximation for the interface potential and disjoining pressure. 
Notice that to first order in non-local effects, the surface tension entering the thin film equation adopts a film thickness dependence which could potentially affect the dynamics. 
Particularly, as far as the parallel correlation length $q_0$ is referred, the non-local effects provide an upper bound equal to the inverse bulk correlation length. 
This could be a significant effect in polymer thin films (c.f. Benet et al. jpc-c 118, 22079, 2014 and the related discussion on dynamical effects Pahlavan et al., jfm, 845, 642, 2018).
}

\item[ \textbf{{Answer}}]
{
We guess that the Referee mentions the fact that the Laplacian of the thickness field, $\nabla^2 h$,
is just a small gradient approximation of the actual local curvature, such that the Laplace contribution to the film pressure should indeed read $\gamma \nabla^2 h/\sqrt{1+|\nabla h|^2}$. This is of course correct, but 
the condition $|\nabla h| \ll 1$ holds true in our system, owing to the very same lubrication approximation,
or, equivalently, to the small contact angles involved; the spinodal wavelength for a homogeneous substrate with
contact angle $\theta_0$ is $\lambda_s = 2\pi/q_0(\theta_0) \approx 70 h_0$. Therefore, the typical gradients
of the thickness field can be estimated as $|\nabla h| \sim h_0/\lambda_s \approx 1/70 \ll 1$ (notice 
that this is, somehow, a worst case scenario since, as we discuss in the text, in the patterned substrates
$\lambda \stackrel{>}{\sim} \lambda_s$).
We have added the following footnote, where we introduce the film pressure:\\
\\
\textcolor{red}{The Laplace pressure is the product of the surface tension 
and the local curvature, therefore its full expression reads $p_L = -\gamma \nabla^2 h/\sqrt{1+|\nabla h|^2}$; 
since we are in the lubrication regime, though, whereby $|\nabla h| \ll 1$, the denominator can be safely neglected 
and the pressure reduces to the form involving only the Laplacian of the thickness field~\cite{Benet2014,juanes2018}}, \\
\\
citing the related papers as a reference.
}
\end{itemize}

### 2022-12-14 coverletter/letter_to_editor.tex
Resubmission PRL

\noindent Dear Editor,\\
\\
\noindent We gratefully thank you for sending us the reports on our manuscript. We are glad to see 
that the Referees agree that the work is interesting and scientifically relevant, with one of them 
(Referee B) inclined to accept it. 
\textcolor{red}{In particular, we would like to underline that not a single 
concern was raised on the physics, namely on the reliability of the results.
On the other hand, we acknowledge that certain points were not explained and/or discussed adequately, so we have put a lot of effort in clarifying all
doubts and concerns.}
We have made, therefore, a major revision taking into account all Referees' reasonable remarks, including novel 
results from new simulations and theoretical derivations (see the new Supplementary Material).
Let us, please, stress further how and why we deem that the present paper meets the Physical
Review Letters criteria of impact and innovation (interest, as we already noted, was acknowledged by the Referees).
We have found a novel effect in the dewetting on substrates with properly tailored time dependent properties, and 
suggested how to exploit it to control the dewetting morphologies, 
\textcolor{red}{even proposing, motivated by one Referee's suggestion, a possible experimental realisation.}
We think that the impact of this discovery is out of question, as witnessed also by the various publications, also in PRL on dewetting and closely related problems
(just to cite but a few recent ones: J.C. Fern\'andez-Toledano et al, ``How wettability controls nanoprinting'',
{\it Phys. Rev. Lett.} {\bf 124} 224503 (2020); A.A. Pahlavan et al,
``Evaporation of binary-mixture liquid droplets: the formation of picoliter pancakelike shapes'', {\it Phys. Rev. Lett.} {\bf 127}, 024501 (2021); 
C. Clavaud et al, ``Modification of the fluctuation dynamics of ultrathin wetting films'', {\it Phys. Rev. Lett.} {\bf 126}, 228004 (2021)).
What it is somehow questionable, instead, is the trustworthiness of some of the Referees in judging a paper on microscale multiphase fluid dynamics: one of 
them (Referee A) ignores the concept of disjoining pressure, confuses dewetting with prewetting and concepts from the physics of free surface flows to wetting.
The main ``argument'' of Referee C against publication is that he/she does not see ``how would the transport of a fluid by rivulets 
surpass the transport by droplets''; but the paper is about controlling morphologies, not about transport.\\
\textcolor{red}{We believe, then, that our manuscript, in its new version, deserves to be brought again to your attention as a contribution to Physical Review Letters, 
confident that it might be now suitable of publication.}\\
\\
With our best regards,\\
the Authors.

>>>>

\vspace*{-3cm}

\noindent Dear Editor,\\

we thank you for sending us the constructive reports on our manuscript. We are glad to see 
that the Referees agree that the work is interesting and scientifically relevant, with one of them 
(Referee B) inclined to accept it.

In particular, we would like to underline that not a single 
concern was raised on the physics, namely on the reliability of the results.
However, we acknowledge that certain points were not explained and/or discussed adequately, and therefore we invested a substantial effort in clarifying all
doubts and concerns.
Our major revision takes into account all Referees' reasonable and constructive remarks, including novel 
results from new simulations and theoretical derivations (see the new Supplementary Material).

Let us, please, stress further how and why we deem that the present paper meets the Physical
Review Letters criteria of impact and innovation (interest, as we already noted, was acknowledged by the Referees).
We found a novel effect in the dewetting on substrates with properly tailored time dependent properties and 
suggest how to exploit it to control the dewetting morphologies. Motivated by a Referee's suggestion, we even propose a possible experimental realisation.
We think that the impact of this discovery is out of question, as witnessed also by the various recent publications on dewetting and closely related problems, which appeared in PRL 
(just to cite but a few recent ones: J.C. Fern\'andez-Toledano et al, ``How wettability controls nanoprinting'',
{\it Phys. Rev. Lett.} {\bf 124} 224503 (2020); A.A. Pahlavan et al,
``Evaporation of binary-mixture liquid droplets: the formation of picoliter pancakelike shapes'', {\it Phys. Rev. Lett.} {\bf 127}, 024501 (2021); 
C. Clavaud et al, ``Modification of the fluctuation dynamics of ultrathin wetting films'', {\it Phys. Rev. Lett.} {\bf 126}, 228004 (2021)).

We would like to point out a few flaws in the referee reports, which in our opinion have led to a misjudgement of our work. Two referees base their criticism on a clear misconception of the aim and background of the paper:
First, Referee A ignores the concept of disjoining pressure, confuses dewetting with prewetting and concepts from the physics of free surface flows to wetting.
Second, the main ``argument'' of Referee C against publication is that he/she does not see ``how would the transport of a fluid by rivulets 
surpass the transport by droplets''. However, as it is clearly stated in the title of our manuscript, the paper is about controlling morphologies, not about transport.

We believe that our manuscript, in its new version, deserves to be brought again to your attention as a contribution to Physical Review Letters and we are 
confident that it might now be suitable for publication.

~\\
With our best regards,\\
Stefan Zitz, Andrea Scagliarini, and Jens Harting
